Providing a Unified Software Environment for Canada’s National Advanced Computing Centers

### 2019-03-21 paper.tex
correction of typos

Written in Python, EasyBlocks define what needs to be done at each step for a given software package. There are generick EasyBlocks, such as {\it ConfigureMake} or {\it CMakeMake}, as well as custom EasyBlocks for packages that have more complicated installation procedures, such as OpenFOAM or PETSc.

@@

Toolchains are a core concept in EasyBuild. They represent a set or subset of a compiler, and MPI implementation, mathematical libraries and CUDA. Having the ability to generate multiple builds of a given software simply by providing a command line argument to change the toolchain has proven unvaluable to our workflow, and has allowed us to recompile hundreds of packages in matter of days when deploying a new version of compiler or a cluster with a new CPU architecture.

>>>>

EasyBlocks are Python classes that define the steps required to install a given software package. There are generick EasyBlocks, such as {\it ConfigureMake} or {\it CMakeMake}, as well as custom EasyBlocks for packages that have more complicated installation procedures, such as OpenFOAM or PETSc.

@@

Toolchains are a core concept in EasyBuild. They represent a set or subset of a compiler, an MPI implementation, mathematical libraries and CUDA. Having the ability to generate multiple builds of a given software simply by providing a command line argument to change the toolchain has proven unvaluable to our workflow, and has allowed us to recompile hundreds of packages in matter of days when deploying a new version of compiler or a cluster with a new CPU architecture.
